---
title: Thesis Title
bibliography:
  - "../Templates/thesis-citations.bib"
  - ../Templates/packages.bib
csl: ../Templates/apa.csl
output:
  pdf_document:
    toc: false
    latex_engine: xelatex
    fig_caption: true
    includes:
      in_header: "../Templates/MtA-Thesis-Preamble.tex"
fontsize: 12pt
geometry:
- margin = 1in
linestretch: 1.5
classoption: oneside
indent: true
editor_options:
  chunk_output_type: inline
always_allow_html: true

# Use nocite to include any citations that aren't included in-text (i.e. R packages)
---

```{r set-global-options, echo=FALSE}
# ------------ Set chunk options --------------------------------------------------------------
# cairo_pdf encodes high-quality plots with searchable text
# Hide chunk warnings to reduce distractions
# comment = NA removes the double hash tags next to chunk output

knitr::opts_chunk$set(
  dev = c("cairo_pdf"),
  dpi = 600,
  fig.align = "center",
  comment = NA,
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r load-libraries, include = FALSE}
# ------------- Load packages ----------------------------------------------------------------------------
# Here are some potentially useful packages to start off with - free feel to delete them if you don't need them
library(here)
library(dplyr) # Data manipulation
library(ggplot2) # Make plots
library(viridis) # Accessible and beautiful colour palettes
library(extrafont) # Required for custom fonts in plots
loadfonts()
library(ggtext) # Required for formatting plot text (e.g. coloured text in title)
library(patchwork) # Required for multi-plot layouts
library(ggsignif) # Required for significance stars and brackets on plots
library(ggh4x) # Required to create nested x-axis labels
library(ggpubr) # Required for significance brackets

# Generate a bibliography of all packages used in this file
# I will use this later to cite all packages that I used in my bibliography

knitr::write_bib(file = here("Templates","packages.bib"))
```

```{r set-plot-options}
# ---------- Set plot theme, colours & sizes --------------------------------------------------------------------------------
# Set save_choice to "yes" if you want to save plots (! this will increase the run time; generally only run this after adding new data)
# To use this, set up an if/else statement with ggsave nested within it

save_choice <- "no"

# Set colours here only for consistency. Here is an example
# Refer to these colours in your ggplot code, for example geom_point(color = my_colours[2]) for blue points.

my_colours <- c("#6600cc", "#0093fb", "#55b323","#ffe70f","#e86c00","#333333", "#411900","#e11584")

# Custom fonts may cause issues depending on what fonts you have in your system
# Troubleshooting steps: 
  # Try changing the font to one that you have on your computer
  # If it does not work, you could always delete 'family = plot_font_family' in the ggplot theme set below
plot_font_family <- "Segoe UI"

# A consistent y-axis enables comparison across multiple experiments, treatments, etc.
# To use this, define variables like y_axis_limit and then use these as limits in coord_cartesian() in your ggplots.

y_axis_limit <- 175
```

```{r set-ggplot2-theme}
# ----------- Set ggplot theme ----------------------------------------------------------------------------------
# You should experiment to find a ggplot theme that works for your project
# Here is an example of defining a ggplot theme.

# This theme increases the axis font sizes and removes the default gray background.
# Requires the extrafont() package (loaded in the load-libraries chunk) for custom font

theme_set(
  theme_classic() %+replace%
    theme(
      text = element_text(
        family = plot_font_family
      ),
      plot.title = element_text(
        color = "black",
        size = 20,
        family = plot_font_family,
        margin = margin(b = 25),
        hjust = 0.5
      ),
      plot.margin = margin(25, 25, 25, 25),
      plot.caption = element_text(
        hjust = 0,
        family = plot_font_family,
        size = 12
      ),
      plot.caption.position = "plot",
      axis.text = element_text(
        size = 12,
        color = "black"
      ),
      axis.title = element_text(
        size = 16,
        face = "bold"
      ),
      axis.title.y = element_text(
        margin = margin(r = 25),
        angle = 90,
        vjust = 0.5
      ),
      axis.title.x = element_text(margin = margin(b = 25, t = 20)),
      axis.ticks = element_blank(),
      strip.background = element_rect(color = NA, fill = NA),
      strip.text = element_text(size = 20)
    )
)
```


\begin{centering}
\begin{spacing}{1}
\Large

by

\LARGE

Author

\end{spacing}
\end{centering}

\large
\vspace*{\fill}

<!-- Although it is not ideal, I am manually setting the linebreaks here. This is to conform to MtA's title page standards -->


\begin{centering}
\begin{spacing}{1}
A thesis submitted to the\\
Department of Biology\\
Mount Allison University\\
in partial fulfillment of the requirements for the\\
Bachelor of Science degree with Honours\\
in Biology

Date

\end{spacing}
\end{centering}


\newpage
\vspace*{\fill}
\large


<!-- The preamble includes \usepackage{adforn}. Adforn enables you to add fancy decorative embellishments. Look up adforn on CTAN to see a list of available symbols. -->

\adforn{20} *COLOPHON* \adforn{48}

\normalsize

This thesis was typeset in R Markdown and the text was set in EB Garamond. The data and code used to produce this document are available at [*https://github.com/christelinda-laureijs/reproducible-thesis*](https://github.com/christelinda-laureijs/reproducible-thesis).

\newpage
\pagenumbering{roman}


# Abstract

Text


\setcounter{tocdepth}{2}
\tableofcontents
\listoffigures


# List of Abbreviations

<!--Tab depth is defined in the preamble through the tabto package-->

DMH \tab{Dorsomedial hypothalamus}\
GABA \tab{Gamma-aminobutyric acid}\
eEPSC \tab{Evoked excitatory post-synaptic current}\
PPR \tab{Paired pulse ratio}\
HNMPA \tab{Hydroxy-2-naphthalenylmethylphosphonic acid}\
PPP \tab{Picropodophyllotoxin}


\cleardoublepage
\normalsize
\pagenumbering{arabic}


# Introduction

# Methods

# Results

# Discussion

# Acknowledgements

# References